---
title: "R Notebook"
output: html_notebook
---

# Load everything

```{r}
source("model.R")  # Load your code.
theme_set(theme_bw())
trained_model <- load_model()
trained_model3 <- read_rds("trained_model3.RDS")
```

```{r}
train_data = read.csv("training.csv") %>% as_tibble() 
x_raw <- train_data %>% select(-claim_amount)
```

```{r}
prices <- predict_premium(trained_model, x_raw)
claims <- predict_expected_claim(trained_model, x_raw)

train_data <- train_data %>% 
  mutate(
    prices_full_xgb = !!prices,
    claims_full_xgb = !!claims
  )
```

```{r}
prices <- predict_premium(trained_model3, x_raw)
claims <- predict_expected_claim(trained_model3, x_raw)

train_data <- train_data %>% 
  mutate(
    prices_train_xgb = !!prices,
    claims_train_xgb = !!claims
  )

```
```{r}
prices <-
  predict_premium(
    model = trained_model3,
    x_raw = x_raw %>% 
      mutate(year == 5, id_policy = paste0("bwah_", row_number()))
    )
claims <-
  predict_expected_claim(
    model = trained_model3,
    x_raw = x_raw %>% 
      mutate(year == 5, id_policy = paste0("bwah_", row_number()))
    )

train_data <- train_data %>% 
  mutate(
    prices_train_gam = !!prices,
    claims_train_gam = !!claims
  )
```

```{r}
prices <-
  predict_premium(
    model = trained_model,
    x_raw = x_raw %>% 
      mutate(year == 5, id_policy = paste0("bwah_", row_number()))
    )
claims <-
  predict_expected_claim(
    model = trained_model,
    x_raw = x_raw %>% 
      mutate(year == 5, id_policy = paste0("bwah_", row_number()))
    )

train_data <- train_data %>% 
  mutate(
    prices_full_gam = !!prices,
    claims_full_gam = !!claims
  )
```

# Check profit margin

```{r}
train_data %>% 
  group_by(year) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  )
```

Profit margin but on chosen market

```{r}
chosen_policy <- train_data %>% 
  left_join(trained_model3$renewal$veh_correction %>% rename(cor_veh = correction)) %>% 
  left_join(trained_model3$renewal$city_correction %>% rename(cor_city = correction)) %>% 
  left_join(trained_model3$renewal$claims_correction %>%
              mutate(correction = 1) %>% 
              rename(cor_claims = correction)) %>%
  mutate(total_cor = cor_veh * cor_city * cor_claims ) %>% 
  filter(total_cor < 1.1) %>% 
  pull(id_policy)
```

```{r}
train_data %>% 
  left_join(trained_model3$renewal$veh_correction %>% rename(cor_veh = correction)) %>% 
  left_join(trained_model3$renewal$city_correction %>% rename(cor_city = correction)) %>% 
  left_join(trained_model3$renewal$claims_correction %>%
              mutate(correction = 1) %>% 
              rename(cor_claims = correction)) %>%
  mutate(total_cor = cor_veh * cor_city * cor_claims ) %>% 
  filter(total_cor < 1.1) %>% 
  filter(year == 4) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = everything()) %>% arrange(desc(value))
```

XGB (renewal) model is better than GAM. But it's normal, since xgb has access to
past claims info.

# Check all features

## drv_age1

```{r}
train_data %>% 
  group_by(drv_age1) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(
    cols = c(starts_with("claims"), starts_with("prices")),
    names_to = "method", values_to = "lr"
  ) %>% 
  filter(drv_age1 < 30) %>% 
  mutate(prices = str_detect(method, "prices")) %>% 
  ggplot(aes(x = drv_age1, y = lr, color = method)) +
  geom_line() + geom_point() +
  ggthemes::scale_color_colorblind() +
  facet_wrap(~prices)
```

```{r}
train_data %>% 
  group_by(year, drv_age1) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = starts_with("claims"), names_to = "method", values_to = "lr") %>% 
  filter(drv_age1 < 30) %>% 
  ggplot(aes(x = drv_age1, y = lr, color = method)) +
  geom_line() + geom_point() +
  ggthemes::scale_color_colorblind() +
  facet_wrap(~year)
```

## Past claims



```{r}
train_data %>% 
  filter(year == 4) %>% 
  left_join(trained_model3$renewal$freq_model$past_claims) %>% 
  group_by(claim_count) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -claim_count) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  mutate(model = name %>% str_remove_all("claims_") %>% str_remove_all("prices_")) %>% 
  ggplot(aes(claim_count, value, color = model)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```

```{r}
train_data %>% 
  filter(year == 4) %>% 
  left_join(trained_model3$renewal$freq_model$past_claims) %>% 
  group_by(claim_count) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  print
  select(claim_count, claims_full_xgb, claims_train_xgb)
```

```{r}
train_data %>% 
  filter(year == 3) %>% 
  left_join(
    train_data %>% filter(year < 3) %>% group_by(id_policy) %>% 
      summarise(claim_count = sum(claim_amount > 0)),
    by = "id_policy"
  ) %>% 
  group_by(claim_count) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  select(claim_count, claims_full_xgb, claims_train_xgb)
train_data %>% 
  filter(year == 4) %>% 
  left_join(
    train_data %>% filter(year < 4) %>% group_by(id_policy) %>% 
      summarise(claim_count = sum(claim_amount > 0)),
    by = "id_policy"
  ) %>% 
  group_by(claim_count) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  select(claim_count, claims_full_xgb, claims_train_xgb)

```

```{r}
l1 <- train_data %>% filter(year == 3) %>% filter(claim_amount > 0) %>% pull(id_policy)
l2 <- train_data %>% filter(year == 2) %>% filter(claim_amount == 0) %>% pull(id_policy)
l3 <- train_data %>% filter(year == 1) %>% filter(claim_amount == 0) %>% pull(id_policy)
ii <- intersect(l1, l2) %>% intersect(l3)

train_data %>% 
  filter(year == 4) %>% 
  filter(id_policy %in% ii) %>% 
  left_join(
    train_data %>% filter(year < 4) %>% group_by(id_policy) %>% 
      summarise(claim_count = sum(claim_amount > 0)),
    by = "id_policy"
  ) %>% 
  group_by(claim_count) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  select(claim_count, claims_full_xgb, claims_train_xgb)

```


```{r}
train_data %>% 
  filter(year == 4) %>% 
  left_join(trained_model$renewal$freq_model$past_claims) %>% 
  group_by(claim_count) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -claim_count) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  mutate(model = name %>% str_remove_all("claims_") %>% str_remove_all("prices_")) %>% 
  ggplot(aes(claim_count, value, color = model)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```

```{r}
train_data %>% 
  filter(year == 4) %>% 
  left_join(trained_model3$renewal$freq_model$past_claims) %>% 
  group_by(claim_count) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -claim_count) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  ggplot(aes(claim_count, value, color = name)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```

## Vehicle

```{r}
train_data %>% 
  filter(year < 4) %>% 
  group_by(vh_make_model) %>% 
  summarise(
    expo = n(),
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  filter(expo > 10) %>% select(-expo) %>% 
  pivot_longer(cols = -vh_make_model) %>% 
  ggplot(aes(name, value)) +
  geom_violin() +
  coord_flip() +
  ylim(0, 2)

```

```{r}
train_data %>% 
  filter(year == 4) %>% 
  group_by(vh_make_model) %>% 
  summarise(
    expo = n(),
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  filter(expo > 10) %>% select(-expo) %>% 
  pivot_longer(cols = -vh_make_model) %>% 
  ggplot(aes(name, value)) +
  geom_violin() +
  coord_flip() +
  ylim(0, 2)

```

## pol_no_claims_discount

```{r}
train_data %>% 
  mutate(
    groupe =
      cut(
        pol_no_claims_discount,
        breaks = c(-1, 0, .01, .02, .05, .1, .2, .3, .4 ,.5, Inf),
        ordered_result = TRUE
        ) %>% 
      as.numeric()
  ) %>% 
  group_by(year, groupe) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    .groups = "drop"
  ) %>% 
  pivot_longer(cols = starts_with("claims"), names_to = "method", values_to = "lr") %>% 
  ggplot(aes(x = groupe, y = lr, color = method)) +
  geom_line() + 
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~year) 
```
## pol_coverage

```{r}
train_data %>% 
  filter(year == 4) %>% 
  # filter(year == 4, id_policy %in% chosen_policy) %>% 
  group_by( pol_coverage) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -pol_coverage) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  mutate(model = name %>% str_remove_all("claims_") %>% str_remove_all("prices_")) %>% 
  ggplot(aes(pol_coverage, value, color = model)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```
Vraiment intéressant celui là.

## pol duration

```{r}
train_data %>% 
  filter(year == 4, id_policy %in% chosen_policy) %>%
  # filter(year == 4) %>% 
  mutate(pol_duration = pmin(pol_duration, 10)) %>% 
  group_by(pol_duration) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -pol_duration) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  mutate(model = name %>% str_remove_all("claims_") %>% str_remove_all("prices_")) %>% 
  ggplot(aes(pol_duration, value, color = model)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```

## pol_pay_Freq

```{r}
train_data %>% 
  filter(year == 4, id_policy %in% chosen_policy) %>%
  # filter(year == 4) %>% 
  group_by(pol_pay_freq) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -pol_pay_freq) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  mutate(model = name %>% str_remove_all("claims_") %>% str_remove_all("prices_")) %>% 
  ggplot(aes(pol_pay_freq, value, color = model)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```
```{r}
train_data %>% count(pol_pay_freq)
```

## drv_age2

```{r}
train_data %>% 
  drop_na(drv_age2) %>% 
  # filter(year == 4, id_policy %in% chosen_policy) %>% 
  filter(year == 4) %>% 
  group_by(drv_age2) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -drv_age2) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  mutate(model = name %>% str_remove_all("claims_") %>% str_remove_all("prices_")) %>% 
  ggplot(aes(drv_age2, value, color = model)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```

## vh value

```{r}
train_data %>% 
  mutate(expo = 1) %>% 
  enablr::add_equal_weight_group(table = ., ratio = vh_value, expo = expo, nb = 20) %>% 
  # filter(year == 4, id_policy %in% chosen_policy) %>% 
  filter(year == 4) %>% 
  group_by(groupe) %>% 
  summarise(
    across(starts_with("claims"), ~sum(claim_amount) / sum(.x)),
    across(starts_with("prices"), ~sum(claim_amount) / sum(.x))
  ) %>% 
  pivot_longer(cols = -groupe) %>% 
  mutate(prices = str_detect(name, "prices")) %>% 
  mutate(model = name %>% str_remove_all("claims_") %>% str_remove_all("prices_")) %>% 
  ggplot(aes(groupe, value, color = model)) +
  geom_point() +
  ggthemes::scale_color_colorblind() +
  geom_hline(aes(yintercept = 1), linetype = 3) +
  facet_wrap(~prices)
```

# Variable importance

```{r}
model <- trained_model$renewal$freq_model

  if (!all.equal(baked_data$unique_id, x_raw$unique_id))
    stop("problem in predict_expected_claim_xgb_base")
  
  gaa2 <- train_data %>%
    mutate(expo = 1) %>% 
    mutate(claim = as.numeric(claim_amount > 0)) %>% 
    mutate(uncapped_amount = claim_amount) %>% 
    # mutate(claim_amount = pmin(claim_amount, capping_threshold)) %>% 
    mutate(unique_id = row_number(), fold = 1) %>% 
    select(unique_id, id_policy, year, claim_amount) %>% 
    arrange(id_policy, year) %>% 
    group_by(id_policy) %>% 
    mutate(
      losses = cumsum(claim_amount), 
      losses = lag(losses, n = 1, default = 0),
      claim_count = cumsum(claim_amount > 0),
      claim_count = lag(claim_count, n = 1, default = 0)
    ) %>% 
    ungroup() %>% 
    mutate(across(c(losses, claim_count), ~.x / pmax(year - 1, 2)))
  df <- 
    left_join(
      train_data %>% mutate(unique_id = row_number()),
      gaa2 %>% select(unique_id, losses, claim_count),
      by = "unique_id"
    )
  
  baked_data <- 
    bake(
      model$recipe,
      new_data = df
    )
  
  baked_data <- 
    left_join(
      baked_data,
      model$df_control,
      by = rec_has_role(model$recipe, "control")
    )
  
  pred_terms <- 
  predict(
    object = model$model, 
    newdata = baked_data %>%
      slice_sample(n = 1e4) %>% 
      select(all_of(rec_has_role(model$recipe, "predictor"))) %>% 
      as.matrix(),
    predcontrib = TRUE
  ) %>% 
    as_tibble()
  
  pred_terms %>% summarise(across(.fns = ~sum(abs(.x)))) %>% 
    pivot_longer(cols = everything()) %>% arrange(desc(value))
```


# Other

Check that all id_policy are hard-coded

```{r}
trained_model$id_policy
trained_model$renewal$freq_model$past_claims
```

# stress test

## check that unknown vehicle gives 50% surcharge

```{r}
pol_info <- x_raw %>%
  filter(id_policy %in% chosen_policy) %>% 
  slice_sample(n = 1)
prem1 <- predict_premium(trained_model, pol_info)
prem2 <- predict_premium(trained_model, pol_info %>% mutate(vh_make_model = "bwah"))

prem2 / prem1

prem1 <- predict_premium(trained_model, pol_info %>% mutate(id_policy = "gaaa"))
prem2 <- predict_premium(trained_model, pol_info %>% mutate(id_policy = "gaaa", vh_make_model = "bwah"))

prem2 / prem1
```


```{r}
prices2 <- predict_premium(trained_model, x_raw %>% mutate(year == 5))
tibble(
  p1 = prices,
  p2 = prices2
) %>% 
  summarise(max = max(abs(p1 - p2)))
```

```{r}
prices2 <- predict_premium(trained_model, x_raw %>% 
                             mutate(year == 5, vh_make_model = "gaaa"))
tibble(
  p1 = prices,
  p2 = prices2
) %>% 
  summarise(ratio = p2 / p1) %>% 
  ggplot(aes(ratio)) + geom_density()
```
```{r}
prices2 <- predict_premium(trained_model, x_raw %>% 
                             mutate(year == 5, population = 1e6))
tibble(
  p1 = prices,
  p2 = prices2
) %>% 
  mutate(ratio = p2 / p1) %>% 
  ggplot(aes(ratio)) + geom_density()
```

```{r}
tibble(
  p1 = prices,
  p2 = prices2
) %>% 
  mutate(ratio = p2 / p1) %>% 
  ggplot(aes(ratio)) + geom_density()
```

```{r}
train_data %>% 
  select(id_policy, year, claim_amount, vh_make_model, town_surface_area, population) %>% 
  mutate(pred_claims = !!claims, pred_premium = !!prices2) %>% 
  summarise(
    lr      = sum(claim_amount) / sum(pred_claims),
    lr_prem = sum(claim_amount) / sum(pred_premium)
  )
```

```{r}
claim2 <- predict_expected_claim(trained_model, x_raw %>% 
                             mutate(year == 5, id_policy = paste0("bwah_", row_number())))
prices2 <- predict_premium(trained_model, x_raw %>% 
                             mutate(year == 5, id_policy = paste0("bwah_", row_number())))
train_data %>% 
  select(id_policy, year, claim_amount, vh_make_model, town_surface_area, population) %>% 
  mutate(pred_claims = !!claim2, pred_premium = !!prices2) %>% 
  left_join(trained_model$renewal$veh_correction %>% rename(cor_veh = correction)) %>% 
  left_join(trained_model$renewal$city_correction %>% rename(cor_city = correction)) %>% 
  left_join(trained_model$renewal$claims_correction %>% rename(cor_claims = correction)) %>% 
  filter(cor_veh * cor_city * cor_claims < 1.1) %>% 
  summarise(
    lr      = sum(claim_amount) / sum(pred_claims),
    lr_prem = sum(claim_amount) / sum(pred_premium)
  )
```


# Renewal model

## Check correction

### Vehicle

```{r}
trained_model$renewal$veh_correction %>% 
  pull(correction) %>% 
  quantile(probs = seq(0, 1, by = .05)) %>% 
  enframe()
```

### Claims

```{r}
trained_model$renewal$claims_correction %>% 
  pull(correction) %>% 
  quantile(probs = seq(0, 1, by = .05)) %>% 
  enframe()
```

```{r}
trained_model$renewal$claims_correction %>% count(correction)
```

### City


```{r}
trained_model$renewal$city_correction %>% 
  pull(correction) %>% 
  quantile(probs = seq(0, 1, by = .05)) %>% 
  enframe()
```

# Zip submission file

```{r}
zip::zip(
  zipfile = "lastday_submission.zip",
  files = c("config.json", "install.R", "model.R",
            "predict.R", "train.R", "trained_model.RDS", "R")
)

```

